### 2017-02-12 ResearchNotes/exps.tex
Adds statistics

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{imgs/fig_0_CTE-UMCED-2_all}
        \label{subfig:exp_001_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{imgs/fig_3_INF7194_2_all}
        \label{subfig:exp_001_3_all}
    \end{subfigure}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{imgs/fig_0_CTE-UMCED-2_cud}
        \label{subfig:exp_001_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{imgs/fig_3_INF7194_2_cud}
        \label{subfig:exp_001_3_cud}
    \end{subfigure}

>>>>

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/exp_001_results/fig_0_CTE-UMCED-2_all}
        \label{subfig:exp_001_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/exp_001_results/fig_3_INF7194_2_all}
        \label{subfig:exp_001_3_all}
    \end{subfigure}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/exp_001_results/fig_0_CTE-UMCED-2_cud}
        \label{subfig:exp_001_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/exp_001_results/fig_3_INF7194_2_cud}
        \label{subfig:exp_001_3_cud}
    \end{subfigure}
